


```{r}
Pre9_pvalue <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9_pvalue_metaboanalyst.xlsx")
Pre6_pvalue <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre6_pvalue_metaboanalyst.xlsx")
Pre3_pvalue <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre3_pvalue_metaboanalyst.xlsx")
Pre0_pvalue <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre0_pvalue_metaboanalyst.xlsx")

Pre9630_pvalue <- Pre9_pvalue %>%
              left_join(Pre6_pvalue, by='path') %>%
              left_join(Pre3_pvalue, by='path') %>%
              left_join(Pre0_pvalue, by='path')

#Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
write_csv(Pre9630_pvalue, 
          file = "/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue_all.csv")


```


```{r}
library(tidyverse)
library(ggbeeswarm)
library(packcircles)
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
```



```{r}
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
Pre9630_pvalue$RawP_9 <- -log10(Pre9630_pvalue$RawP_9)

Pre9_bubble <- ggplot(Pre9630_pvalue, aes(Pre9, RawP_9, fill = RawP_9)) +
 geom_quasirandom(aes(size = Impact_9), shape = 21, 
                  alpha = c(ifelse(abs(Pre9630_pvalue$RawP_9) > 1.3, 0.9, 0.25)), 
                  groupOnX = FALSE, priority = "random", width =0.15) +
 geom_text_repel(data=subset(Pre9630_pvalue, path == c('Bile secretion' , 'Phe metabolism', 'Cys/Met metabolism',
                                                       'Retrograde EC signaling', 'Choline metabolism')),
    aes(x = Pre9, y = RawP_9,label=path,point.size = Impact_9),
    size = 5, # font size in the text labels
    point.padding = 0, # additional padding around each point
    min.segment.length = 0, # draw all line segments
    max.time = 1, max.iter = 1e5, # stop after 1 second, or after 100,000 iterations
    box.padding = 0.3 # additional padding around each text label
  ) +
  scale_size(range = c(2,10)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme_pubr() +
  scale_fill_gradient2(low = "#ffffff", high = "#4DBBD5B2") +
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  theme(legend.position = "top", 
        axis.line=element_line(size=0.75),
        axis.ticks=element_line(size=0.75)) +
  scale_y_continuous(limits=c(0, 5), breaks=seq(0,5,1))
Pre9_bubble
```



```{r}
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
Pre9630_pvalue$RawP_9 <- -log10(Pre9630_pvalue$RawP_9)

Pre9_bubble <- ggplot(Pre9630_pvalue, aes(Pre9, RawP_9, fill = RawP_9)) +
 geom_quasirandom(aes(size = Impact_9), shape = 21, 
                  alpha = c(ifelse(abs(Pre9630_pvalue$RawP_9) > 1.3, 0.9, 0.25)), 
                  groupOnX = FALSE, priority = "random", width =0.15) +
 geom_text_repel(data=subset(Pre9630_pvalue, path == c('Bile secretion' , 'Phe metabolism', 'Cys/Met metabolism',
                                                       'Retrograde EC signaling', 'Choline metabolism')),
           aes(x = Pre9, y = RawP_9,label=path), 
           min.segment.length =5, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,
           max.overlaps = Inf) +
  scale_size(range = c(2,10)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme_pubr() +
  scale_fill_gradient2(low = "#ffffff", high = "#4DBBD5B2") +
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  theme(legend.position = "top", 
        axis.line=element_line(size=0.75),
        axis.ticks=element_line(size=0.75)) +
  scale_y_continuous(limits=c(0, 5), breaks=seq(0,5,1))
Pre9_bubble
```

```{r}
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
Pre9630_pvalue$RawP_6 <- -log10(Pre9630_pvalue$RawP_6)

Pre6_bubble <- ggplot(Pre9630_pvalue, aes(Pre6, RawP_6, fill = RawP_6)) +
 # geom_beeswarm(aes(size = Impact_9), shape = 21, alpha = .8, groupOnX = FALSE, priority = "random") +
   geom_quasirandom(aes(size = Impact_6), shape = 21, 
                    alpha = c(ifelse(abs(Pre9630_pvalue$RawP_6) > 1.3, 0.9, 0.25)), 
                    groupOnX = FALSE, priority = "random", width =0.15) +
  geom_text_repel(data=subset(Pre9630_pvalue, RawP_6 > 1.3),
           aes(x = Pre6, y = RawP_6,label=path), 
           min.segment.length = 0, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,
           max.overlaps = Inf) +
  scale_size(range = c(2,10)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme_pubr() +
  scale_fill_gradient2(low = "#ffffff", high = "#4DBBD5B2") +
  coord_cartesian(clip = "off")  +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  theme(legend.position = "right", 
        axis.line=element_line(size=0.75),
        axis.ticks=element_line(size=0.75)) +
  scale_y_continuous(limits=c(0, 5), breaks=seq(0,5,1))
Pre6_bubble
```



```{r}
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
Pre9630_pvalue$RawP_3 <- -log10(Pre9630_pvalue$RawP_3)

Pre3_bubble <- ggplot(Pre9630_pvalue, aes(Pre3, RawP_3, fill = RawP_3)) +
 # geom_beeswarm(aes(size = Impact_9), shape = 21, alpha = .8, groupOnX = FALSE, priority = "random") +
  geom_quasirandom(aes(size = Impact_3), shape = 21, 
                    alpha = c(ifelse(abs(Pre9630_pvalue$RawP_3) > 1.3, 0.9, 0.25)), 
                    groupOnX = FALSE, priority = "random", width =0.15) +
  geom_text_repel(data=subset(Pre9630_pvalue, RawP_3 > 1.3),
           aes(x = Pre3, y = RawP_3,label=path), 
           min.segment.length = 0, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,
           max.overlaps = Inf) +
  scale_size(range = c(2,10)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme_pubr() +
  scale_fill_gradient2(low = "#ffffff", high = "#4DBBD5B2") +
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  theme(legend.position = "right", 
        axis.line=element_line(size=0.75),
        axis.ticks=element_line(size=0.75)) +
  scale_y_continuous(limits=c(0, 5), breaks=seq(0,5,1))
Pre3_bubble
```


```{r}
Pre9630_pvalue<- read_csv("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre9630_pvalue2.csv")
Pre9630_pvalue   <- Pre9630_pvalue |> na.omit()
Pre9630_pvalue$RawP_0 <- -log10(Pre9630_pvalue$RawP_0)

Pre0_bubble <- ggplot(Pre9630_pvalue, aes(Pre0, RawP_0, fill = RawP_0)) +
 # geom_beeswarm(aes(size = Impact_9), shape = 21, alpha = .8, groupOnX = FALSE, priority = "random") +
  geom_quasirandom(aes(size = Impact_0), shape = 21, 
                   alpha = c(ifelse(abs(Pre9630_pvalue$RawP_0) > 1.3, 0.9, 0.25)), 
                   groupOnX = FALSE, priority = "random", width =0.15) +
  geom_text_repel(data=subset(Pre9630_pvalue, RawP_0 > 1.3),
           aes(x = Pre0, y = RawP_0,label=path),
           min.segment.length = 0, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,
           max.overlaps = Inf) +
  scale_size(range = c(2,10)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme_pubr() +
  scale_fill_gradient2(low = "#ffffff", high = "#4DBBD5B2") +
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  theme(legend.position = "right", 
        axis.line=element_line(size=0.75),
        axis.ticks=element_line(size=0.75)) +
  scale_y_continuous(limits=c(0, 5), breaks=seq(0,5,1))

Pre0_bubble
```


```{r}
bubble <- ggarrange(Pre9_bubble + rremove("xlab"), 
                Pre6_bubble + rremove("ylab") + rremove("xlab") + rremove("y.axis") + rremove("y.ticks") + rremove("y.text"), 
                Pre3_bubble + rremove("ylab") + rremove("xlab") + rremove("y.axis") + rremove("y.ticks") + rremove("y.text"),
                Pre0_bubble + rremove("ylab") + rremove("xlab") + rremove("y.axis") + rremove("y.ticks") + rremove("y.text"), 
                ncol = 4, nrow = 1, legend = "none", align = "hv")
bubble
#ggsave("PM_volcano.png", plot=PM_volcano, path=figures, height=5, width=14, units=c("in"), dpi=300)
```





rownames(Pre9630_pvalue) <- Pre9630_pvalue$path
df <- Pre9630_pvalue[c('Bile secretion','Phe metabolism', 'Cys/Met metabolism', 'Retrograde EC signaling', 'Choline metabolism', 'Val/Leu/Ile biosynthesis'),]

```{r}
Pre9630_pvalue <- as.data.frame(Pre9630_pvalue)
rownames(Pre9630_pvalue) <- Pre9630_pvalue$path

df <- Pre9630_pvalue[c('Bile secretion','Phe metabolism', 'Cys/Met metabolism', 'Retrograde EC signaling', 'Choline metabolism', 'Val/Leu/Ile biosynthesis'),]

df <- df %>% 
  mutate(Pre9 = recode(Pre9, 
                          "Pre9" = "9"),
         Pre6 = recode(Pre6, 
                          "Pre6" = "6"),
         Pre3 = recode(Pre3, 
                          "Pre3" = "3"),
         Pre0 = recode(Pre0, 
                          "Pre0" = "0"))
head(df)

df <- df[,c('path', 'RawP_9','RawP_6', 'RawP_3', 'RawP_0')]
       
melt_df <- melt(df, na.rm = FALSE, id = c("path"))

melt_df <- melt_df %>% 
  mutate(variable = recode(variable, 
                          "RawP_9" = "-9",
                          "RawP_6" = "-6",
                          "RawP_3" = "-3",
                          "RawP_0" = "0"))

melt_df$variable <- as.numeric(melt_df$variable)
 
melt_df$value <- -log10(melt_df$value)

melt_df <- melt_df %>% 
  mutate(variable = recode(variable, 
                          "1" = "-9",
                          "2" = "-6",
                          "3" = "-3",
                          "4" = "0"))

melt_df$variable <- as.numeric(melt_df$variable)

head(melt_df)
```



```{r}
melt_df_Bile <- melt_df[melt_df$path == 'Bile secretion',]
melt_df_Bile

pd <- position_dodge(0.00) 
Bile <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Bile Secretion\n ") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
  guides(color = "none")
Bile




melt_df_Bile <- melt_df[melt_df$path == 'Phe metabolism',]
melt_df_Bile

pd <- position_dodge(0.00) 
Phe <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Phenylalanine\nMetabolism") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
  guides(color = "none")
Phe



melt_df_Bile <- melt_df[melt_df$path == 'Cys/Met metabolism',]
melt_df_Bile

pd <- position_dodge(0.00) 
Cys <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Cysteine/Methionine\nMetabolism") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
  guides(color = "none")
Cys





melt_df_Bile <- melt_df[melt_df$path == 'Retrograde EC signaling',]
melt_df_Bile

pd <- position_dodge(0.00) 
Retro <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Retrograde Endocannabinoid\nSignaling") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
   guides(color = "none")
Retro



melt_df_Bile <- melt_df[melt_df$path == 'Choline metabolism',]
melt_df_Bile

pd <- position_dodge(0.00) 
Choline <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Choline\nMetabolism") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
   guides(color = "none")
Choline


melt_df_Bile <- melt_df[melt_df$path == 'Val/Leu/Ile biosynthesis',]
melt_df_Bile

pd <- position_dodge(0.00) 
Val <- ggplot(melt_df_Bile, 
           aes(x = variable, y = value)) + 
  geom_line(size = 1.3,
            color = '#4DBBD5FF') +
  geom_point(color = "black",
             size = 4, 
             shape = 21,
             stroke = 1.3,
             fill= '#4DBBD5FF') +
  theme_pubr() +
  scale_x_continuous(breaks=seq(-9, 9, 3)) +
  ylab(bquote(~-Log[10]~ 'P')) +
  theme(text = element_text(size=14),
       plot.title = element_text(hjust = 0.5, face = "bold"),
       axis.title.y = element_text(vjust = +1),
       legend.position = "none") +
       ggtitle("Valine-Leucine-Isoleucine\nBiosythesis") +
       rremove("legend.title") +
  scale_y_continuous(limits=c(0,5),
                     labels = label_number(accuracy = 0.1), 
                     breaks=seq(0,5, by = 1)) + 
  coord_cartesian(clip = "off") +
  geom_hline(yintercept=1.3, linetype="dashed", 
                color = "black", size=0.5) +
  scale_fill_manual(values=c('#4DBBD5FF')) +
  scale_color_manual(values=c("4DBBD5FF")) + 
   guides(color = "none")
Val

```




```{r}
Path <- ggarrange(Bile, Phe, Cys, Retro, Choline, Val, 
                ncol = 2, nrow = 3, legend = "none", align = "hv")
Path
ggsave("Pathways.png", plot=Path, path=figures, height=12, width=10, units=c("in"), dpi=300)
```







```{r}
# Bile secretion
selfcontained.test(pvalue=c(0.01963,	0.00002,	0.01775,	0.00236), weight=NA,p_permu=NA) 
```

```{r}
# Phenylalanine metabolism
selfcontained.test(pvalue=c(0.00437,	0.05829,	0.01187,	0.00086), weight=NA,p_permu=NA) 
```

```{r}
# Cysteine and methionine metabolism
selfcontained.test(pvalue=c(0.01598,	0.03963,	0.00500,	0.02422), weight=NA,p_permu=NA) 
```

```{r}
# Retrograde endocannabinoid signaling
selfcontained.test(pvalue=c(0.01473,	0.01238,	0.08398,	0.00230), weight=NA,p_permu=NA) 
```

```{r}
# Choline metabolism in cancer
selfcontained.test(pvalue=c(0.06815,	0.00826,	0.02966,	0.02257), weight=NA,p_permu=NA) 
```

```{r}
# Valine, leucine and isoleucine biosynthesis
selfcontained.test(pvalue=c(0.00008,	0.03793,	0.15402,	0.00974), weight=NA,p_permu=NA) 
```

```{r}
# NF-kappa B signaling pathway
selfcontained.test(pvalue=c(0.06234,	0.00708,	0.02694,	0.11529), weight=NA,p_permu=NA) 
```

```{r}
# Histidine metabolism
selfcontained.test(pvalue=c(0.12240,	0.04617,	0.00916,	0.05757), weight=NA,p_permu=NA) 
```

```{r}
# Aldosterone synthesis and secretion
selfcontained.test(pvalue=c(0.08532,	0.00254,	0.16911,	0.02893), weight=NA,p_permu=NA) 
```

```{r}
# ABC transporters
selfcontained.test(pvalue=c(0.07373,	0.15828,	0.00090,	0.08124), weight=NA,p_permu=NA) 
```

```{r}
# Carbohydrate digestion and absorption
selfcontained.test(pvalue=c(0.02604,	0.20794,	0.07629,	0.06350), weight=NA,p_permu=NA) 
```

```{r}
# Glycerophospholipid metabolism
selfcontained.test(pvalue=c(0.13804,	0.24361,	0.01340,	0.00934), weight=NA,p_permu=NA) 
```

```{r}
# Endocrine and other factor-regulated calcium reabsorption
selfcontained.test(pvalue=c(0.01566,	0.03266,	0.31508,	0.04502), weight=NA,p_permu=NA) 
```

```{r}
# Linoleic acid metabolism
selfcontained.test(pvalue=c(0.08680,	0.00406,	0.04816,	0.27248), weight=NA,p_permu=NA) 
```

```{r}
# Kaposi sarcoma-associated herpesvirus infection
selfcontained.test(pvalue=c(0.08327,	0.02250,	0.03015,	0.28666), weight=NA,p_permu=NA) 
```

```{r}
# Adipocytokine signaling pathway
selfcontained.test(pvalue=c(0.13986,	0.21634,	0.07988,	0.06653), weight=NA,p_permu=NA) 
```

```{r}
# Thyroid hormone synthesis
selfcontained.test(pvalue=c(0.19799,	0.09541,	0.11631,	0.09759), weight=NA,p_permu=NA) 
```

```{r}
# Glycine, serine and threonine metabolism
selfcontained.test(pvalue=c(0.00107,	0.00369,	0.42827,	0.08906), weight=NA,p_permu=NA) 
```

```{r}
# Sphingolipid metabolism
selfcontained.test(pvalue=c(0.02425,	0.19957,	0.36040,	0.00741), weight=NA,p_permu=NA) 
```

```{r}
# Pentose and glucuronate interconversions
selfcontained.test(pvalue=c(0.00729,	0.08214,	0.42469,	0.08738), weight=NA,p_permu=NA) 
```

```{r}
# Sphingolipid signaling pathway
selfcontained.test(pvalue=c(0.32242,	0.19860,	0.04973,	0.03826), weight=NA,p_permu=NA) 
```

```{r}
# Insulin secretion
selfcontained.test(pvalue=c(0.052771, 	0.10236, 	0.4561, 0.017067), weight=NA,p_permu=NA) 
```
```{r}
# cAMP signaling pathway
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Adrenergic signaling in cardiomyocytes
selfcontained.test(pvalue=c(0.04872,	0.10970,	0.25708,	0.22075), weight=NA,p_permu=NA) 
```

```{r}
# AGE-RAGE signaling pathway in diabetic complications
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Arginine biosynthesis
selfcontained.test(pvalue=c(0.31775,	0.09026,	0.03004,	0.21762), weight=NA,p_permu=NA) 
```

```{r}
# Mineral absorption
selfcontained.test(pvalue=c(0.00674,	0.63441,	0.01647,	0.01242), weight=NA,p_permu=NA) 
```

```{r}
# Arginine and proline metabolism
selfcontained.test(pvalue=c(0.00083,	0.18121,	0.00798,	0.51160), weight=NA,p_permu=NA) 
```

```{r}
# Salivary secretion
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Insulin resistance
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Tyrosine metabolism
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Pyrimidine metabolism
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```

```{r}
# Gastric acid secretion
selfcontained.test(pvalue=c(), weight=NA,p_permu=NA) 
```






```{r}
# Arginine and proline metabolism
selfcontained.test(pvalue=c(0.00083,	0.18121,	0.00798,	0.51160), weight=NA,p_permu=NA) 
```





```{r}
selfcontained.test<-function(pvalue,weight=NA,p_permu=NA) 
{  
  if (sum(is.na(pvalue))>0) {stop ("Error: pvalue is NA.")}
  if (min(pvalue)<0) {stop ("Error: pvalue is negative.")}
  if (max(pvalue)>1) {stop ("Error: pvalue is >1.")}
  if (is.na(weight)[1]) {weight=rep(2, length(pvalue))}
  if (length(pvalue)!=length(weight)){stop ("Error: length(pvalue)!=length(weight).")}
  if (min(weight)<0) {stop ("Error: weight is negative.")}
  if (!is.na(p_permu)[1]) {if (nrow(p_permu)!=length(pvalue)) {stop ("Error: nrow(p_permu)!=length(pvalue)")}}
  if (!is.na(p_permu)[1]) {if (nrow(p_permu)!=length(pvalue)) {stop ("Error: nrow(p_permu)!=length(pvalue)")}}
  
  et<-sum(weight)
  fun2<-function(x){qchisq(1-x,df=weight)}
  if (is.na(p_permu)[1]) {vart<-2*sum(weight)} else {vart<-sum(cov(t(apply(p_permu,2,fun2))))}
  v<-2*et^2/vart
  c<-vart/2/et
  T<-sum(qchisq(1-pvalue,weight)) 
  if (is.na(p_permu)[1]) {cor_p<-diag(length(pvalue))} else {cor_p<-cor(t(p_permu))}
  return(list("significance level for combining pvalues"=pchisq(T/c, v, lower.tail=FALSE), "correlation among pvalues"=cor_p))
}
```

