

```{r}
library(ggplot2)
df <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre0369_PM_promise.xlsx")

colors = c("#e6194b", "#3cb44b", "#ffe119", "#4363d8", "#f58231", 
           "#911eb4", "#46f0f0", "#f032e6", "#bcf60c", "#fabebe", 
           "#008080", "#e6beff", "#9a6324", "#fffac8")

ggplot(data=df, aes(x=time, y = impact, colour = Pathway)) +
   geom_smooth(method = "loess",
              se = FALSE,
              formula = 'y ~ x') +
  labs(title = " ") +
  theme_minimal() +
  scale_color_manual(values=colors) +
   geom_labelsmooth(aes(
    x = time, y = impact, group = Pathway, colour = Pathway, label = Pathway
  ),
  hjust = .5
  ) +
  theme(legend.position = "none")
  
  
  
  geom_text(data = df %>% filter(time == last(time)), aes(label = Pathway, 
                                                           x = time + 0.5, 
                                                           y = impact, 
                                                           color = Pathway)) + 
          guides(color = FALSE) + theme_bw() + 
          scale_x_continuous(breaks = scales::pretty_breaks(9))
```







```{r}
library(ggplot2)
df <- read_excel("/bigrock/FurmanLab/DataRepository/promise/Misc/Pre0369_PM_promise.xlsx")

ggplot(df, aes(x = time, y = impact, group=Pathway, color=Pathway)) +
  geom_smooth(method = "loess",
              se = FALSE,
              formula = 'y ~ x',
              span = 0.8) +
  stat_smooth(se=FALSE, geom="area",
              method = 'loess', alpha=.5,
              span = 0.8,aes(fill=Pathway)) + 
  theme_minimal() + scale_fill_npg() + scale_color_npg()
```
ggplot(df, aes(time, impact, pathway)) + 
  geom_area(data = df, fill = "#80C020", alpha = 0.35) + 
  geom_line(data = df, colour = "#80C020", size = 1.2) +
  geom_point(shape = 16, size = 4.5, colour = "#80C020") +
  geom_point(shape = 16, size = 2.5, colour = "white") +
  theme_bw() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.border       = element_blank(),
        axis.line.x        = element_line(),
        text               = element_text(size = 15),
        plot.margin        = margin(unit(c(20, 20, 20, 20), "pt")),
        axis.ticks         = element_blank(),
        axis.text.y        = element_text(margin = margin(0,15,0,0, unit = "pt"))) +
  scale_alpha_identity() + labs(x="",y="") 

