


```{r}
countData <- read_excel("/bigrock/FurmanLab/DataRepository/promise/metabolomics/promise_metabolomics_all_trans.xlsx")
countData <- countData[!startsWith(countData$metabolite, "X-"),]
countData  <- countData %>% distinct(metabolite, .keep_all = TRUE)
df <- data.frame(countData)
cols <- sapply(df, is.numeric)
df[cols] <- 1000*df[cols]
head(df)
df <- cbind(df[,1], sapply(df[,-1], as.integer))
colnames(df)[1] <- "metabolite"
df <- as.data.frame(df)


### comparison 1
prepostOGTT_pre6 <- df |>
select("metabolite", 
       "X2249.0.Y3", "X2249.120.Y3", "X2321.0.Y3", "X2321.120.Y3",
       "X2280.0.Y3", "X2280.120.Y3", "X2127.0.Y3", "X2127.120.Y3",
       "X2089.0.Y3", "X2089.120.Y3", "X2099.0.Y3", "X2099.120.Y3",
       "X2261.0.Y3", "X2261.120.Y3", "X1397.0.Y3", "X1397.120.Y3",
       "X2070.0.Y3", "X2070.120.Y3", "X1300.0.Y3", "X1300.120.Y3",
       "X2220.0.Y3", "X2220.120.Y3", "X1152.0.Y3", "X1152.120.Y3")

df <- cbind(df[,1], sapply(prepostOGTT_pre6[,-1], as.numeric))
colnames(df)[1] <- "metabolite"
prepostOGTT_pre6 <- as.data.frame(df)

prepostOGTT_pre6$X2249.0.Y3 <- as.numeric(prepostOGTT_pre6$X2249.0.Y3)
prepostOGTT_pre6$X2249.120.Y3 <- as.numeric(prepostOGTT_pre6$X2249.120.Y3)
prepostOGTT_pre6$X2321.0.Y3 <- as.numeric(prepostOGTT_pre6$X2321.0.Y3)
prepostOGTT_pre6$X2321.120.Y3 <- as.numeric(prepostOGTT_pre6$X2321.120.Y3)
prepostOGTT_pre6$X2280.0.Y3 <- as.numeric(prepostOGTT_pre6$X2280.0.Y3)
prepostOGTT_pre6$X2280.120.Y3 <- as.numeric(prepostOGTT_pre6$X2280.120.Y3)
prepostOGTT_pre6$X2127.0.Y3 <- as.numeric(prepostOGTT_pre6$X2127.0.Y3)
prepostOGTT_pre6$X2127.120.Y3 <- as.numeric(prepostOGTT_pre6$X2127.120.Y3)
prepostOGTT_pre6$X2089.0.Y3 <- as.numeric(prepostOGTT_pre6$X2089.0.Y3)
prepostOGTT_pre6$X2089.120.Y3 <- as.numeric(prepostOGTT_pre6$X2089.120.Y3)
prepostOGTT_pre6$X2099.0.Y3 <- as.numeric(prepostOGTT_pre6$X2099.0.Y3)
prepostOGTT_pre6$X2099.120.Y3 <- as.numeric(prepostOGTT_pre6$X2099.120.Y3)
prepostOGTT_pre6$X2261.0.Y3 <- as.numeric(prepostOGTT_pre6$X2261.0.Y3)
prepostOGTT_pre6$X2261.120.Y3 <- as.numeric(prepostOGTT_pre6$X2261.120.Y3)
prepostOGTT_pre6$X1397.0.Y3 <- as.numeric(prepostOGTT_pre6$X1397.0.Y3)
prepostOGTT_pre6$X1397.120.Y3 <- as.numeric(prepostOGTT_pre6$X1397.120.Y3)
prepostOGTT_pre6$X2070.0.Y3 <- as.numeric(prepostOGTT_pre6$X2070.0.Y3)
prepostOGTT_pre6$X2070.120.Y3 <- as.numeric(prepostOGTT_pre6$X2070.120.Y3)
prepostOGTT_pre6$X1300.0.Y3 <- as.numeric(prepostOGTT_pre6$X1300.0.Y3)
prepostOGTT_pre6$X1300.120.Y3 <- as.numeric(prepostOGTT_pre6$X1300.120.Y3)
prepostOGTT_pre6$X2220.0.Y3 <- as.numeric(prepostOGTT_pre6$X2220.0.Y3)
prepostOGTT_pre6$X2220.120.Y3 <- as.numeric(prepostOGTT_pre6$X2220.120.Y3)
prepostOGTT_pre6$X1152.0.Y3 <- as.numeric(prepostOGTT_pre6$X1152.0.Y3)
prepostOGTT_pre6$X1152.120.Y3 <- as.numeric(prepostOGTT_pre6$X1152.120.Y3)

prepostOGTT_pre6$X2249.fc <- (prepostOGTT_pre6$X2249.120.Y3 / prepostOGTT_pre6$X2249.0.Y3)
prepostOGTT_pre6$X2321.fc <- (prepostOGTT_pre6$X2321.120.Y3 / prepostOGTT_pre6$X2321.0.Y3)
prepostOGTT_pre6$X2280.fc <- (prepostOGTT_pre6$X2280.120.Y3 / prepostOGTT_pre6$X2280.0.Y3)
prepostOGTT_pre6$X2127.fc <- (prepostOGTT_pre6$X2127.120.Y3 / prepostOGTT_pre6$X2127.0.Y3)
prepostOGTT_pre6$X2089.fc <- (prepostOGTT_pre6$X2089.120.Y3 / prepostOGTT_pre6$X2089.0.Y3)
prepostOGTT_pre6$X2099.fc <- (prepostOGTT_pre6$X2099.120.Y3 / prepostOGTT_pre6$X2099.0.Y3)
prepostOGTT_pre6$X2261.fc <- (prepostOGTT_pre6$X2261.120.Y3 / prepostOGTT_pre6$X2261.0.Y3)
prepostOGTT_pre6$X1397.fc <- (prepostOGTT_pre6$X1397.120.Y3 / prepostOGTT_pre6$X1397.0.Y3)
prepostOGTT_pre6$X2070.fc <- (prepostOGTT_pre6$X2070.120.Y3 / prepostOGTT_pre6$X2070.0.Y3)
prepostOGTT_pre6$X1300.fc <- (prepostOGTT_pre6$X1300.120.Y3 / prepostOGTT_pre6$X1300.0.Y3)
prepostOGTT_pre6$X2220.fc <- (prepostOGTT_pre6$X2220.120.Y3 / prepostOGTT_pre6$X2220.0.Y3)
prepostOGTT_pre6$X1152.fc <- (prepostOGTT_pre6$X1152.120.Y3 / prepostOGTT_pre6$X1152.0.Y3)

prepost.fc_6 <- prepostOGTT_pre6 |>
select("metabolite", 
       "X2249.fc", "X2321.fc",
       "X2280.fc", "X2127.fc",
       "X2089.fc", "X2099.fc",
       "X2261.fc", "X1397.fc",
       "X2070.fc", "X1300.fc",
       "X2220.fc", "X1152.fc")

metaData6 <- data.frame (
      id  = 
      c("X2249.fc", "X2321.fc",
       "X2280.fc", "X2127.fc",
       "X2089.fc", "X2099.fc",
       "X2261.fc", "X1397.fc",
       "X2070.fc", "X1300.fc",
       "X2220.fc", "X1152.fc"),
      
      Site = 
      c("Control", "Convert", 
        "Control", "Convert",
        "Control", "Convert",
        "Control", "Convert",
        "Control", "Convert",
        "Control", "Convert"))

countData  <- prepost.fc_6 %>% distinct(metabolite, .keep_all = TRUE)
df <- data.frame(countData)
cols <- sapply(df, is.numeric)
df[cols] <- 1000*df[cols]
head(df)
df <- cbind(df[,1], sapply(df[,-1], as.integer))
colnames(df)[1] <- "metabolite"
countData <- as.data.frame(df)

df <- cbind(as.data.frame(countData[,1]), 
            sapply(countData[,-1], as.numeric))
colnames(df)[1] <- "metabolite"
countData <- as.data.frame(df)
countData <- countData  |> na.omit()

countData <- as.data.frame(countData)
metaData <- as.data.frame(metaData6)
dds <- DESeqDataSetFromMatrix(countData=countData, colData=metaData, design=~Site, tidy = TRUE)
# Sex + ... Site 
dds <- DESeq(dds)
res <- results(dds)
res <- results(dds, contrast=c("Site","Convert", "Control"))
```


```{r}
 keyvals.colour <- ifelse(
    res$log2FoldChange < -0 & res$pvalue < 0.05, "#3C5488B2",
      ifelse(res$log2FoldChange > 0 & res$pvalue < 0.05, "#DC0000B2",
        'black'))
  keyvals.colour[is.na(keyvals.colour)] <- 'black'
  names(keyvals.colour)[keyvals.colour == "#DC0000B2"] <- 'high'
  names(keyvals.colour)[keyvals.colour == 'black'] <- 'ns'
  names(keyvals.colour)[keyvals.colour == "#3C5488B2"] <- 'low'

res$metabolite <- rownames(res)

res1 <- as.data.frame(res)

res2 <- filter(res1, metabolite %in% c(
                    'cholate','chenodeoxycholate', 'glycocholate', 'glycochenodeoxycholate', 'glyco-beta-muricholate**', 
                    'glycochenodeoxycholate glucuronide (1)', 'glycocholate-glucuronide (1)', 'glycochenodeoxycholate 3-sulfate',
                    'taurocholate', 'taurochenodeoxycholate', 'deoxycholate', 'isoursodeoxycholate', 'isoursodeoxycholate sulfate (1)', 
                    'lithocholate', 'ursodeoxycholate', '7-ketodeoxycholate', 'lithocholate sulfate (1)', 'hyocholate', '7-ketolithocholate',
                    'glycodeoxycholate', 'glycolithocholate', 'glycoursodeoxycholate', 'glycodeoxycholate 3-sulfate', 'glycohyocholate', 
                    'glycolithocholate sulfate*', 'taurochenodeoxycholate', 'taurodeoxycholate', 'taurolithocholate',
                     'tauroursodeoxycholate', 'taurolithocholate 3-sulfate', 'tauro-beta-muricholate'))

PrePost6_OGTT <- EnhancedVolcano(res,
                      title = NULL,
                      subtitle = NULL,
                      lab = rownames(res),
                      x = 'log2FoldChange',
                      y = 'pvalue',
                      xlab = bquote(~Log[2]~ '  fold change'),
                      pCutoff = 0.05,
                      FCcutoff = 0,
                      labSize = 0,
                      labCol = 'black',
                      labFace = 'bold',
                      pointSize = 2,
                      boxedLabels = FALSE,
                      legendPosition = 'none',
                      legendLabSize = 11,
                      legendIconSize = 4.0,
                      drawConnectors = TRUE,
                      arrowheads = FALSE,
                      colCustom = keyvals.colour,
                      colAlpha = c(ifelse(abs(res$pvalue) < 0.05, 0.5, 0.2)),
                      caption = NULL,
                      selectLab =  c('glycocholate', 'glycochenodeoxycholate', 'glyco-beta-muricholate**', 
                    'glycochenodeoxycholate glucuronide (1)', 'glycocholate-glucuronide (1)', 'glycochenodeoxycholate 3-sulfate',
                    'taurocholate', 'taurochenodeoxycholate',
                     'lithocholate sulfate (1)', 'hyocholate',
                    'glycodeoxycholate', 'glycoursodeoxycholate', 'glycodeoxycholate 3-sulfate', 'glycohyocholate', 
                    'taurochenodeoxycholate', 'taurodeoxycholate', 'taurolithocholate',
                     'tauroursodeoxycholate', 'taurolithocholate 3-sulfate', 'tauro-beta-muricholate'),
                       max.overlaps = 50,
                      maxoverlapsConnectors =50,
                      widthConnectors = 0.3, xlim = c(-6, 6),ylim = c(0, -log10(10e-6)))
PrePost6_OGTT <- PrePost6_OGTT + theme_pubr() +
  annotate("rect", xmin = -6, xmax = -0.1, ymin = -log10(0.04), ymax = -log10(10e-6), alpha = .05) +
  annotate("rect", xmin = 0.1, xmax = 6, ymin = -log10(0.04), ymax = -log10(10e-6), alpha = .05) +
  geom_point(size = 2.5, alpha = .9, na.rm = T, shape = 21, colour = "black") +
  geom_text_repel( aes(label=metabolite), size=3, colour='white' ) +
  geom_text_repel( aes(label=metabolite), size=3, colour='black' )
PrePost6_OGTT
ggsave("Pre6_OGTT_Volcano_DEM.png", plot=PrePost6_OGTT, path=figures, height=5, width=5, units=c("in"), dpi=300)
```



```{r}
PrePost6_OGTT <- EnhancedVolcano(res,
                      title = NULL,
                      subtitle = NULL,
                      lab = rownames(res),
                      x = 'log2FoldChange',
                      y = 'pvalue',
                      xlab = bquote(~Log[2]~ '  fold change'),
                      pCutoff = 0.05,
                      FCcutoff = 0,
                      labSize = 3,
                      pointSize = 2,
                      boxedLabels = FALSE,
                      legendPosition = 'none',
                      legendLabSize = 11,
                      legendIconSize = 4.0,
                      drawConnectors = TRUE,
                      arrowheads = FALSE,
                      colCustom = keyvals.colour,
                      colAlpha = c(ifelse(abs(res$pvalue) < 0.05, 0.5, 0.2)),
                      caption = NULL,
                       max.overlaps = 0,
                      maxoverlapsConnectors =0,
                      widthConnectors = 0.3, xlim = c(-6, 6),ylim = c(0, -log10(10e-6)))
PrePost6_OGTT <- PrePost6_OGTT + theme_pubr() +
  annotate("rect", xmin = -6, xmax = -0.1, ymin = -log10(0.04), ymax = -log10(10e-6), alpha = .05) +
  annotate("rect", xmin = 0.1, xmax = 6, ymin = -log10(0.04), ymax = -log10(10e-6), alpha = .05) +
  geom_point(size = 2.5, alpha = .9, na.rm = T, shape = 21, colour = "black") +
  geom_text(data=res2, aes(x = log2FoldChange, y = pvalue, label=metabolite))
  
  

PrePost6_OGTT
# ggsave("Pre6_OGTT_Volcano_DEM.png", plot=PrePost6_OGTT, path=figures, height=7, width=7, units=c("in"), dpi=300)
```
```
           min.segment.length =5, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,


  
  geom_text(data=subset(res, metabolite == c('glycocholate', 'glycochenodeoxycholate', 'glyco-beta-muricholate**', 
                    'glycochenodeoxycholate glucuronide (1)', 'glycocholate-glucuronide (1)', 'glycochenodeoxycholate 3-sulfate',
                    'taurocholate', 'taurochenodeoxycholate',
                     'lithocholate sulfate (1)', 'hyocholate',
                    'glycodeoxycholate', 'glycoursodeoxycholate', 'glycodeoxycholate 3-sulfate', 'glycohyocholate', 
                    'taurochenodeoxycholate', 'taurodeoxycholate', 'taurolithocholate',
                     'tauroursodeoxycholate', 'taurolithocholate 3-sulfate', 'tauro-beta-muricholate')),
           size=4,
           colour ='black',
           max.overlaps = Inf) 




 geom_text_repel(data=subset(Pre9630_pvalue, metabolite == c('glycocholate', 'glycochenodeoxycholate', 'glyco-beta-muricholate**', 
                    'glycochenodeoxycholate glucuronide (1)', 'glycocholate-glucuronide (1)', 'glycochenodeoxycholate 3-sulfate',
                    'taurocholate', 'taurochenodeoxycholate',
                     'lithocholate sulfate (1)', 'hyocholate',
                    'glycodeoxycholate', 'glycoursodeoxycholate', 'glycodeoxycholate 3-sulfate', 'glycohyocholate', 
                    'taurochenodeoxycholate', 'taurodeoxycholate', 'taurolithocholate',
                     'tauroursodeoxycholate', 'taurolithocholate 3-sulfate', 'tauro-beta-muricholate')),
           aes(x = Pre9, y = RawP_9,label=path), 
           min.segment.length =5, 
           max.time = 1, max.iter = 1e5, 
           box.padding = 0.3,
           max.overlaps = Inf) +
